---
title: "Spelling Bee Help"
# author: "Mohit Shukla"
# date: '2022-Apr-23'
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(words)
library(tidyverse)
library(shiny)
```



This document is created as a help or solution to the NYTimes [Spelling Bee Game](https://www.nytimes.com/puzzles/spelling-bee). In the game, the user has to create words that contain at least 4 letters, and must include the central letter. 

This tool helps the user list all such words. The user just has to Select a Central Letter and fill the other 6 Letters.



```{r formulas, echo=FALSE}
`%!in%` <- Negate(`%in%`)
L = 4       # min length of words

W = words::words
W$word = W$word %>% str_to_upper
W = W[W$word_length>=max(L,1),1] %>% unlist
```

If you need more solving tips, [this article can help](https://www.nytimes.com/2021/12/09/crosswords/spellingbee-tips.html).


## Select Inputs

```{r inputs, echo=FALSE}
inputPanel(
  selectizeInput(inputId="L2", label=h3("Select Central Letter"), LETTERS, selected=NULL, multiple=FALSE, options=NULL),
  selectizeInput(inputId="L1", label=h3("Select 6 Other Letters"), LETTERS, selected=NULL, multiple=TRUE, options=NULL)
)
```


## Output 

```{r output, echo=FALSE}
renderText({
  L3 = LETTERS[which(LETTERS %!in% c(input$L1,input$L2))]
  W = W[!grepl(paste0(L3, collapse = '|'), W, ignore.case = TRUE)]
  W = W[grepl(input$L2, W, ignore.case = TRUE)]
  W
})
```


